Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-20 paper/paper.qmd
commit text changes

## Predicted Election Winner By State

@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state on a map [@usmap], based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.

@@

## Summary of Predicted Election Results by State

@tbl-modelresults further breaks down the polling data by state, showing the average polling percentages for each candidate and the predicted win probability for Trump. For example, in Florida, Trump’s polling average is 53%, and his predicted win probability is almost certain at 99.93%. Conversely, in Michigan, Harris leads with an average of 46.27% of the vote, resulting in a 96.77% predicted probability that she will win the state.

>>>>

## Predicted Election Winner By State
@fig-statemap shows the predicted winner of the 2024 US Presidential Election by state on a map [@usmap], based on a logistic regression model using aggregated polling data for Donald Trump and Kamala Harris. States where Trump is predicted to win are shown in red, while states where Harris is predicted to win are displayed in blue. States in gray represent missing or incomplete polling data, where predictions were not possible. According to the model, Trump is expected to win key states, including Florida, Missouri, and Montana, while Harris is forecasted to lead in Michigan, Virginia, and Pennsylvania.

@@

## Summary of Predicted Election Results by State
@tbl-modelresults further breaks down the polling data by state, showing the average polling percentages for each candidate and the predicted win probability for Trump. For example, in Florida, Trump’s polling average is 53%, and his predicted win probability is almost certain at 99.93%. Conversely, in Michigan, Harris leads with an average of 46.27% of the vote, resulting in a 96.77% predicted probability that she will win the state.
